---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

# inet

Higher-order Internet Protocol ('IP') Address Methods

## Description

A collection of tools and methods that expand upon the functionality
of the 'iptools' package. 

## NOTE

Currently uses `Remotes:` in the `DESCRIPTION` since it depends on the _development version_ of `iptools`.

## What's Inside The Tin

The following functions are implemented:

- `as.ipv4`:	Convert a character vector of IP(v4) addresses into an 'ipv4' object
- `as.numeric`:	Convert an IPv4 object to an numeric vector
- `decode_toredo`:	Decode Toredo IPv6 strings into components
- `enrich`:	Enrich a collection of IP addresses with country and AS information
- `in_addr_arpa`:	Convert IPv4 addresses into in-addr.arpa format
- `ipv4_to_ipv6`:	Perform 6-to-4 and 4-to-6 addressing
- `ipv6_to_ipv4`:	Perform 6-to-4 and 4-to-6 addressing
- `octets`:	Turn an IPv4 object or a character vector of IPv4 addresses into a data frame of octets

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/iptools")
devtools::install_github("hrbrmstr/inet")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(inet)
library(tidyverse)

# current verison
packageVersion("inet")

```

```{r}
set.seed(19216811)

x <- iptools::ip_random(20)
x <- as.ipv4(x)

as.numeric(x)

enrich(x)

octets(x)

in_addr_arpa(x)
```

### [RFC 3056](https://tools.ietf.org/html/rfc3056>) 6-to-4 / 4-to-6 encoding

```{r}
set.seed(19216811)

data_frame(
  src = iptools::ip_random(10),
  to6 = ipv4_to_ipv6(src),
  to4 = ipv6_to_ipv4(to6),
  equal = (src == to4)
)
```

### [RFC 4380](https://tools.ietf.org/html/rfc4380) Teredo IPv6 Decoding

```{r}
decode_toredo("2001:0000:4136:e378:8000:63bf:3fff:fdd2")
```
