---
output: rmarkdown::github_document
---

# inet

Higher-order Internet Protocol ('IP') Address Methods

## Description

A collection of tools and methods that expand upon the functionality
of the 'iptools' package. Only 'IPv4' addresses are currently supported.

## What's Inside The Tin

- `as.ipv4`:	Convert a character vector of IP(v4) addresses into an 'ipv4' object
- `as.numeric`:	Convert an IPv4 object to an numeric vector
- `enrich`:	Enrich a collection of IP addresses with country and AS information
- `in_addr_arpa`:	Convert IPv4 addresses into in-addr.arpa format
- `octets`:	Turn an IPv4 object or a character vector of IPv4 addresses into a data frame of octets

The following functions are implemented:

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/inet")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(inet)
library(tidyverse)

# current verison
packageVersion("inet")

```

```{r}
set.seed(19216811)

x <- iptools::ip_random(20)
x <- as.ipv4(x)

as.numeric(x)

enrich(x)

octets(x)

in_addr_arpa(x)
```